Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is an extended abstract of \citet{CompetingBandits-merged}, which in turn subsumes conference papers \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}.}

### 2020-09-04 journal paper/content/related_work.tex
Minor space-saving edits.

\xhdr{Exploration.} Multi-armed bandits (\emph{MAB}) is an elegant and tractable abstraction for tradeoff between \emph{exploration} and \emph{exploitation}: essentially, between acquisition and usage of information. MAB problems have been studied for many decades by researchers from computer science, operations research, statistics and economics, generating a vast and multi-threaded literature.  The most relevant thread concerns MAB with stochastic rewards and no auxiliary structure, which is the problem faced by each principal in our model (more on this in Appendix~\ref{app:bg}). The basic model has been extended in many different directions, with a considerable amount of work on each: \eg payoffs with a specific structure (\eg combinatorial, linear, convex or Lipschitz), payoff distributions that change over time, and auxiliary payoff-relevant signals. This literature is covered in several dedicated monographs,
\citep{Gittins-book11,Bubeck-survey12,slivkins-MABbook,LS19bandit-book}.%
\footnote{\citet{Gittins-book11} covers Markovian formulations, the other three are concerned with regret-minimization.}
Various connections to economics and game theory are detailed in 
books \citep{CesaBL-book,slivkins-MABbook} and surveys \citep{Bergemann-survey06,Horner-survey16}. A discussion of industrial applications can be found in \citep{DS-arxiv}.

>>>>

\xhdr{Exploration.} Multi-armed bandits (\emph{MAB}) is an elegant and tractable abstraction for tradeoff between \emph{exploration} and \emph{exploitation}: essentially, between acquisition and usage of information. MAB problems have been studied for many decades by researchers from computer science, operations research, statistics and economics, generating a vast and multi-threaded literature.  The most relevant thread concerns MAB with stochastic rewards and no auxiliary structure, which is the problem faced by each principal in our model (see Appendix~\ref{app:bg}). The basic model has been extended in many different directions, with a considerable amount of work on each: \eg payoffs with a specific structure (\eg combinatorial, linear, convex or Lipschitz), payoff distributions that change over time, and auxiliary payoff-relevant signals. This literature is covered in dedicated monographs,
\citep{Gittins-book11,Bubeck-survey12,slivkins-MABbook,LS19bandit-book}.%
\footnote{\citet{Gittins-book11} covers Markovian formulations, the other three are concerned with regret-minimization.}
Various connections to economics and game theory are detailed in 
books \citep{CesaBL-book,slivkins-MABbook} and surveys \citep{Bergemann-survey06,Horner-survey16}. Industrial applications are discussed in \citep{DS-arxiv}.
